### 2022-06-15 main/chapter_2ljets.tex
remove May; improve intro paragraph

This section describes the designs and rationales behind the control,
validation, and signal regions of the $\twoljets$ analysis.

>>>>

The remainder of this section describes the designs of the control,
validation, and signal regions of the $\twoljets$ analysis, along with some
reasoning behind those designs.
